Data for wells in North Dakota's Bakken region come from the Oil and Gas Division of the North Dakota Industrial Commission (NDIC), the regulator for the drilling and production of oil and gas in North Dakota.\footnote{NDIC's well data are available at \href{https://www.dmr.nd.gov/oilgas}{Official Portal for North Dakota State Government}.} NDIC-providing well data include a complete index of all wells permitted in North Dakota. The data contains basic information for each well, such as the type of well, completion and spud dates, location, the first and the current operator names, and targeting pool. Individual well's projection and injection histories, including producing days during each month, are also contained in the data. 

Detailed well completion data are also obtained from NDIC.\footnote{Using Form 6, Well Completion or Recompletion Report, filed by operators, NDIC has developed the detailed data.} The data contain how much water and proppant were consumed during well simulations.

The regulatory body also provides well-level survey data. The survey data include directions and lengths of legs in a well. Using the leg-related information in the data, we compute the total length of horizontal drillings in an individual well. 

The sample used throughout this paper consists of 24,520 horizontal wells that targeted the Bakken pool.\footnote{The Bakken pool includes Bakken, Three Forks, and Sanish formations.} Summary statistics for those wells are presented in Table \ref{Table:Summary-Statistics-for-Horizontal-Wells}.
