Utilizing a panel DID identification strategy, I first measure the impact of the TOU prices on 30-minute-interval household electricity consumption. To obtain the Average Treatment Effect (ATE) for each half-hour interval, I estimate the following specification:
\begin{equation}
\begin{split}
    \textit{kWh}_{itw} \ 
    & = \ \beta_{w} \mathbb{1}\big[ \text{Treatment \& Post} \big]_{it} \ + \ \alpha_{iw} \ + \ \gamma_{tw} \ + \ \delta_{m} \ + \ \epsilon_{itw}
\end{split}
\label{Eq:Model-Specification_Half-Hourly-Average-Treatment-Effects}
\end{equation}
The term $kWh_{itw}$ is the electricity consumption by household $i$ on the day $t$ during the half-hourly time window $w$. The indicator variable $\mathbb{1}\big[ \text{Treatment \& Post} \big]_{it}$ is equal to 1 only if household $i$ is in the treatment group and the day $t$ is in the treatment period. The terms $\alpha_{iw}$, $\gamma_{tw}$, and $\delta_{m}$ are household-by-half-hourly-interval, day-of-sample-by-half-hourly-time-window, and month-of-year fixed effects, respectively. In the specification, the point estimates of $\beta_{w}$, representing the ATE for each 30-minute interval $w$, are the parameters of interest. I cluster the standard errors at the household and the day of experiment levels to correct for serial correlation.

Figure \ref{Figure:Half-Hourly-Average-Treatment-Effects} summarizes the estimated ATEs in the form of a time profile. As already demonstrated in \cite{Peaking-Interest:How-Awareness-Drives-the-Effectiveness-of-Time-of-Use-Electricity-Pricing_Prest_2020}, peak hours (i.e., from 5:00 p.m. to 7:00 p.m.), during which the inefficiency of fixed flat rate tariff is greatly intensified, show dominant electricity savings. Although household electricity consumption altered considerably in two-hour-length intervals just before and after the peak rate period (i.e., from 3:00 p.m. to 5:00 p.m. and from 7:00 p.m. to 9:00 p.m., respectively), the TOU prices are unlikely to provoke significant changes in households' consumption behavior, except the immediate meter-reading period, in the intervals. But it is difficult to believe that the participating households managed their electricity consumption precisely along with the price increases in the peak rate period. Rather, it is more likely that they preemptively adjusted their consumption behavior in the hours leading up to and following the peak rate period. For this reason, in the following empirical analysis, I continually focus on household electricity demand responses to the time-varying prices in the three intervals. 