My empirical results obviously illustrate that the effectiveness of the TOU tariffs, as measured by the amount of the induced electricity savings, nonlinearly varies with daily HDDs. As discussed, the total electricity savings caused by the deployment of TOU pricing consists of two elements: the savings from electricity consumption for non-temperature-control uses and those from electricity consumption for temperature-control uses. By definition, the savings originating from non-for-heating electricity consumption are independent of daily HDDs. Hence, the nonlinearity in the effectiveness of the TOU structures is utterly attributable to the other source of electricity savings, electricity consumption for heating which Figure XYZ confirms. 

The nonlinear relationship between the amount of TOU-price-causing electricity savings and daily HDDs indicates an interesting characteristic of the tariff structure: the day-varying effects of TOU pricing on residential electricity consumption. Daily HDDs, one of the critical determinants of for-heating-relevant electricity consumption, fluctuate day by day. Therefore, it is intuitive that in response to daily changing household heating needs, the total amount of TOU-price-inducing electricity savings also alters every day. 

The day-varying effectiveness of TOU electricity pricing suggests an implication in connection with Real-Time Pricing (RTP), a type of time-varying electricity tariff structure.\footnote{\cite{Household-Responses-to-Time-Varying-Electricity-Prices_Harding-and-Sexton_2017} provides a detailed description of various kinds of time-varying electricity tariff structures.} Contrary to TOU pricing, rates typically change hourly under RTP. So compared to TOU pricing, RTP has an advantage in reflecting generation costs contemporaneously. Economists, therefore, prefer RTP to TOU pricing. But because TOU-tariff-inducing electricity savings covariate with daily HDDs, TOU electricity pricing can somewhat emulate the favorable feature of RTP, especially on days with moderate temperatures. For example, on typical winter days in Ireland, Tariff Group A's heating-associated electricity savings in the peak rate period were more than half of the total savings under the TOU program. In other words, the time-varying rate structure already induced substantial reductions in electricity consumption according to across-day variations in generation costs, even though there were only within-day price variations under the structure. Consequently, in that case, the additional gains obtained by switching to RTP might not be significant as economists have expected. 

