This section delves into the analysis of two distinct economic frameworks. In Section \ref{C3-SubSection:A-Limitation-of-AKS-style-Model}, the optimal drilling and extraction model developed in \cite{Hotelling-under-Pressure_AKS_2018} is reformulated by introducing heterogeneity in resource quality. And it is shown that the recast model cannot justify the empirically observed simultaneous drilling of well locations with varying quality levels. In the subsequent portions of this section, a continuous-time Discrete Choice Dynamic Programming (DCDP) model for oil and gas extraction is developed, successfully articulating the simultaneous drilling of horizontal wells with heterogeneous quality.

% A Limitation of AKS-style Model
\subsection{A Limitation of AKS-style Model}
\label{C3-SubSection:A-Limitation-of-AKS-style-Model}
\input{04_Chapter-3/03_A-DCDP-Model-in-Continuous-Time/A-DCDP-Model-in-Continuous-Time_A-Limitation-of-AKS-style-Model.tex}

% Setup
\subsection{Setup}
\label{C3-SubSection:Setup}
\input{04_Chapter-3/03_A-DCDP-Model-in-Continuous-Time/A-DCDP-Model-in-Continuous-Time_Setup.tex}

% Social Planner's Problem
\subsection{Social Planner's Problem and Necessary Conditions}
\label{C3-SubSection:Social-Planners-Problem-and-Necessary-Conditions}
\input{04_Chapter-3/03_A-DCDP-Model-in-Continuous-Time/A-DCDP-Model-in-Continuous-Time_Social-Planners-Problem-and-Necessary-Conditions.tex}

\subsubsection{Implications of Necessary Conditions}
\label{C3-SubSubSection:Necessary-Conditions}
\input{04_Chapter-3/03_A-DCDP-Model-in-Continuous-Time/A-DCDP-Model-in-Continuous-Time_Social-Planners-Problem-and-Necessary-Conditions_Implications.tex}

% Firm's Problem
\subsection{Firm's Problem}
\label{C3-SubSection:Firms-Problem}
In this section, we develop the firm's problem under the settings of our DCDP model in continuous time. We first introduce additionally required building blocks. In particular, we integrate heterogeneity in the quality of well sites into the problem. Following \cite{Estimation-of-Dynamic-Discrete-Choice-Models-in-Continuous-Time_ABBE_2016}, we formulate the value function for a given well site. And then, utilizing the value function, we show that the oil market clears. In addition, we formulate firm-level optimal paths by aggregating the firm's well-level drilling decisions. 

\subsubsection{Firm's Decisions on Drilling Well Sites}
\label{C3-SubSubSection:Firms-Decisions-on-Drilling-Well-Sites}
\input{04_Chapter-3/03_A-DCDP-Model-in-Continuous-Time/A-DCDP-Model-in-Continuous-Time_Firms-Problem.tex}
