Exploiting the sharp Regression Discontinuity (RD) design described earlier, I estimate the following econometric specification to measure how SMUD residential customers respond, in terms of their electricity consumption in a billing month (i.e., Period 1), to the discontinuous change in the marginal prices due to exceeding the lower base usage quantity in the previous billing month (i.e., Period 0):
\input{02_Chapter-1/00C_Equations/Equation_RD-Econometric-Model.tex}
The dependent variable $ADC_{i, 1}$ is the average daily consumption by household $i$ in Period 1. $\widebar{NC}_{i, 0}$ corresponds to the running variable, household $i$'s normalized consumption in Period 0:
\input{02_Chapter-1/00C_Equations/Equation_Normalized-Consumption.tex}
where $kWh_{i, 0}$ and $BUQ_{i, 0}$ are, in Period 0, household $i$'s aggregate electricity consumption and the lower base usage quantity, respectively. The binary indicator variable $\mathbb{1}[Treatment]_{i, 0}$ is equal to 1 only if household $i$'s aggregate electricity consumption in Period 0 exceeded the lower base usage quantity:
\input{02_Chapter-1/00C_Equations/Equation_Treatment-Status-Determination-Rule.tex}
For $f\left( \widebar{NC}_{i, 0} \right)$, which is a continuous function of $\widebar{NC}_{i, 0}$, I utilize a variety of functional forms to show the robustness of my estimates. $\boldsymbol{X}$ are covariates, such as average daily Cooling Degree Days (CDDs) and average daily Heating Degree Days (HDDs). $\delta_{ym}$ is billing year-by-month fixed effects (FEs).\footnote{For a given billing observation, the mid-date of the observation determines the billing month-by-year.} The last term $\epsilon_{i, 0}$ is a stochastic error term. In this model, the coefficient of interest $\beta$ captures the treatment effect. I cluster the standard errors at the household ID as well as billing year-by-month levels to allow correlations across households in a given month.

In the specification, each household's average daily electricity consumption, instead of the aggregate consumption, in a billing cycle is utilized as the dependent variable. My sample contains household-level monthly billing records. But because of the fact that each billing month consists of a different number of days, I use each billing month's average daily consumption for my empirical analysis. For the same reason, average daily CDDs and HDDs are exploited in later analysis. 