In this research, weather data are an essential element. The main interest of most TOU papers has been to measure how consumers respond to TOU prices or the heterogeneity in their responsiveness across different information stimuli. Hence, those studies usually do not control temperature variations directly. For example, \cite{The-Effect-of-Information-on-TOU-Electricity-Use:An-Irish-Residential-Study_Pon_2017} and \cite{Peaking-Interest:How-Awareness-Drives-the-Effectiveness-of-Time-of-Use-Electricity-Pricing_Prest_2020}, which also exploited the CER experiment dataset, added weak-of-sample and month-by-year fixed effects (FEs) to their specifications, respectively, in order to control for variations in electricity usage due to seasonal changes. On the other hand, the primary objective of this paper is to decompose the TOU-price-inducing demand reductions into two parts--reductions in temperature-control and non-temperature-control uses. Since the electricity consumption for temperature-control uses is driven by weather, especially temperatures, it is necessary to link the 30-minute interval consumption data and reliable weather data with an appropriate level of resolution. 

The electricity savings associated with for-heating electricity consumption are disaggregated using average daily temperatures from the total savings resulting from the introduction of TOU prices. More granular temperatures, like hourly temperatures, are not a dominant determinant of electricity demand for temperature-control uses at a point in time. It is not easy to believe that households adjust their electricity consumption according to ever-changing outside temperatures elaborately and instantly. Furthermore, as shown in Figure \ref{Figure:Average-Hourly-Electricity-Consumption-by-Time-of-Day}, their electricity demand is the lowest in the early morning, the coldest time of the day. Considering those two points, I measure the TOU-tariff-inducing reductions in electricity consumption conditional on the average heating need in a given day. 

I exploit hourly temperature data for the Dublin airport weather station, provided by Met \'{E}ireann, Ireland's National Meteorological Service, to compute average daily temperatures. There is no available location information in the published CER experiment dataset for privacy and security reasons. Therefore, it is impossible to match a participant's consumption data with the weather data of the closest weather monitoring station to him. But fortunately, in Ireland, temperatures do not vary much across areas for a given day. As demonstrated in Table \ref{Table:Correlations-in-Average-Daily-Temperatures-among-Weather-Stations}, the temperature correlations between the Dublin station and stations near densely populated cities are evident. Because of the positive correlations, I use the mean daily temperatures obtained by averaging the Dublin airport station's hourly temperatures as the representative temperatures in the following analysis.

Using the average daily temperatures, I calculate daily Heating Degree Days (HDDs). Instead of 65 degrees of Fahrenheit ($^{\circ}F$), a normal base temperature in the United States, 60$^{\circ}F$ is utilized to compute daily HDDs, according to \cite{The-Impacts-of-Climate-Change-on-Domestic-Natural-Gas-Consumption-in-the-Greater-Dublin-Region_Liu-and-Sweeney_2012}. Figure \ref{Figure:Distribution-of-Heating-Degree-Days-during-the-Experiment-Period} shows that many days in the treatment period had lower average daily temperatures than the lowest one during the baseline period. The evolving pattern of heating-purpose demand for electricity on days with extreme temperatures could be significantly different under distinct rate structures--flat and TOU rates. If this is true, the lack of counterfactual consumption observations will cause bias in the measured impact of introducing TOU pricing on household electricity consumption. So, I drop observations for those days in the treatment period when constructing the sample to address the potential threat to the identification. 
